---
title: "Mini Project 1"
subtitle: "SDS 192"
author: "Jenny Ding,Victoria Chen,Niya Dai"
date: "`r format(Sys.Date(), '%B %e, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    fig_width: 7
    fig_height: 6
    fig_caption: true
    theme: lumen
    df_print: paged
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  echo = TRUE
)
library(tidyverse)
library(sds192)
```

##Diamonds are a Girl's (Costly) Friend
As we can see from the first 10 rows of the data, diamond value is characterized by the 4c's: carat, cut, color and clarity. Each variable evaluates diamonds from a distinct dimension. From Hollywood tabloid headlines, we seem to think that the bigger the diamond, the more bankroll an actor makes, and perhaps, a happier marriage. However, is that the case? We investigate into other variables that determine a diamond's value, and what it means to have a flawless diamond. 

```{r}
diamonds
```


##Color
We color coded diamond color to the line color for an intuitive interpretation. In nature, colorless diamonds are the most rare, so their price are higher per carat. However, from this graph, we see that price actually declines with increasing carat for the most colorless stone, while diamond with a faint tint has the best growth potential. We assume this happens since **D-J** are all on the near colorless to colorless scale, it is hard for the human eye to see the difference. When people are evaluating carat for color grade, they may prefer a larger carat than a premium colorless stone. So we see a steady rise for **J** graded diamonds. 

```{r}
diamonds_plot <- ggplot(data=diamonds, aes(x=carat, y=price)) +
  scale_color_brewer(palette="PuBuGn")+
  labs(title="Prices of over 50,000 round cut diamonds",
       subtitle = "Effect of color",
       color="Color from Colorless to Near Colorless", 
       xlab(aes(color="white"))) + 
  scale_x_continuous(name="Weight of diomond (carat)")+
  scale_y_continuous(name="Price of diamonds (US dollars)")+
  geom_smooth(aes(color=color), se = F)+
  theme(panel.background = element_rect(fill = "#1C1C1D"),
        plot.background = element_rect(fill = "#1C1C1D"),
        panel.grid =element_line("#464646"), 
        axis.title = element_text(color="white"), 
        plot.title=element_text(color="white"), 
        plot.subtitle = element_text(color="white"),
        legend.background = element_rect(fill = "#1C1C1D", color ="#1C1C1D" ), 
        legend.text = element_text(color = "white"), 
        legend.title = element_text(color = "white"), 
        legend.key = element_rect(fill ="black", color="#1C1C1D"),
        legend.box.background = element_rect(color = "white"))
diamonds_plot
```


#Clarity
As we can see from the graph, the highest clarity characteristic **IF** can fetch the same price as the lowest **I1** at just over 2 carats. We also see that once we step into the **S** category price increase slows down dramatically. We assume that perfect clarity is a very rare characteristic in natural diamonds. 

```{r}
diamonds_plot <- ggplot(data=diamonds, aes(x=carat, y=price)) +
  scale_color_brewer(palette="PuBuGn")+
  labs(title="Prices of over 50,000 round cut diamonds",
       subtitle = "Effect of Clarity",
       color="Clarity from worst to best", 
       xlab(aes(color="white"))) + 
  scale_x_continuous(name="Weight of diomond (carat)")+
  scale_y_continuous(name="Price of diamonds (US dollars)")+
  geom_smooth(aes(color=clarity), se = F)+
  theme(panel.background = element_rect(fill = "#1C1C1D"),
        plot.background = element_rect(fill = "#1C1C1D"),
        panel.grid =element_line("#464646"), 
        axis.title = element_text(color="white"), 
        plot.title=element_text(color="white"), 
        plot.subtitle = element_text(color="white"),
        legend.background = element_rect(fill = "#1C1C1D", color ="#1C1C1D" ), 
        legend.text = element_text(color = "white"), 
        legend.title = element_text(color = "white"), 
        legend.key = element_rect(fill ="black", color="#1C1C1D"),
        legend.box.background = element_rect(color = "white"))
diamonds_plot
```

## Word count

```{r word_count, message=FALSE, echo=FALSE}
text_stats()
```

## Standards

In this assignment, we attempted the following [standards](https://beanumber.github.io/sds192/standards.html):

- `r standard_button("markdown")`: We met the Markdown standard because we...
- `r standard_button("aesthetics")`: We met the Aesthetics standard because we...


