---
title: "SDS 192 Assignment"
subtitle: "SDS 192"
author: "Jenny Ding, Victoria Chen,Niya Dai"
date: "`r format(Sys.Date(), '%B %e, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    fig_width: 7
    fig_height: 6
    fig_caption: true
    theme: lumen
    df_print: paged
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  echo = TRUE
)
library(tidyverse)
library(sds192)
library(ggthemes)
library(RColorBrewer)
```

# Diamonds are a Girl's (Costly) Friend
## Data Frame 
As we can see from the first 10 rows of the data, diamond value is characterized by the 4c's: carat, cut, color and clarity. Each variable evaluates diamonds from a distinct dimension. From Hollywood tabloid headlines, we seem to think that the bigger the diamond, the more bankroll an actor makes, and perhaps, a happier marriage. However, is that the case? We investigate into other variables that determine a diamond's value, and what it means to have a flawless diamond. 
```{r}
diamonds
```

## Clarity
As we can see from the graph, the highest clarity characteristic **IF** can fetch the same price as the lowest **I1** at just over 2 carats. We also see that once we step into the **S** category price increase slows down dramatically. We assume that perfect clarity is a very rare characteristic in natural diamonds. 
```{r}
diamonds_plot <- ggplot(data=diamonds, aes(x=carat, y=price)) +
  scale_color_brewer(palette="PuBuGn")+
  labs(title="Prices of over 50,000 round cut diamonds",
       subtitle = "Effect of clarity on price of diamonds at each weight.",
       color="Clarity from worst to best", 
       xlab(aes(color="white"))) + 
  scale_x_continuous(name="Weight of diomond (carat)")+
  scale_y_continuous(name="Price of diamonds (US dollars)")+
  geom_smooth(aes(color=clarity), se = F)+
  theme(panel.background = element_rect(fill = "#1C1C1D"),
        plot.background = element_rect(fill = "#1C1C1D"),
        panel.grid =element_line("#464646"), 
        axis.title = element_text(color="white"), 
        plot.title=element_text(color="white"), 
        legend.background = element_rect(fill = "#1C1C1D", color ="#1C1C1D" ), 
        legend.text = element_text(color = "white"), 
        legend.title = element_text(color = "white"), 
        legend.key = element_rect(fill ="black", color="#1C1C1D"),
        legend.box.background = element_rect(color = "white"))
diamonds_plot

```


## Color
We color coded diamond color to the line color for an intuitive interpretation. In nature, colorless diamonds are the most rare, so their prices are higher per carat. However, from this graph, we see that price actually declines with increasing carat for the most colorless stone, while diamond with a faint tint has the best growth potential. We assume this happens since **D-J** are all on the near colorless to colorless scale, it is hard for the human eye to see the difference. When people are evaluating carat for color grade, they may prefer a larger carat than a premium colorless stone. So we see a steady rise for **J** graded diamonds. 
```{r}
diamonds_plot <- ggplot(data=diamonds, aes(x=carat, y=price, color = cut)) +
  scale_color_brewer(palette="PuBuGn")+
  labs(title="Prices of over 50,000 round cut diamonds",
       subtitle = "Effect of color on price of diamonds at each weight.",
       caption = "According to jewelry retailer Blue Nile, the color grade is arranged from Colorless (D, E, and F) to Near-Colorless (G, H, I, J). Near-Colorless diamonds contain small traces of color, but can’t be seen very easily with the naked eye.",
       color="Color from Colorless to Near Colorless", 
       xlab(aes(color="white"))) + 
  scale_x_continuous(name="Weight of diomond (carat)")+
  scale_y_continuous(name="Price of diamonds (US dollars)")+
  geom_smooth(aes(color=color), se = F)+
  theme(panel.background = element_rect(fill = "#1C1C1D"),
        plot.background = element_rect(fill = "#1C1C1D"),
        panel.grid =element_line("#464646"), 
        axis.title = element_text(color="white"), 
        plot.title=element_text(color="white"), 
        plot.subtitle = element_text(color="white"),
        plot.caption = element_text(color="#858585", face="italic"),
        legend.background = element_rect(fill = "#1C1C1D", color ="#1C1C1D" ), 
        legend.text = element_text(color = "white"), 
        legend.title = element_text(color = "white"), 
        legend.key = element_rect(fill ="black", color="#1C1C1D"),
        legend.box.background = element_rect(color = "white")) 
diamonds_plot
```


## Word count

```{r word_count, message=FALSE, echo=FALSE}
text_stats()
```

## Standards

In this assignment, we attempted the following [standards](https://beanumber.github.io/sds192/standards.html):

- `r standard_button("markdown")`: In this assignment, we investigated the variables that affect the value of diamonds. In particular, we selected clarity and color, and cut as variables to see how they affect the value of diamonds. We used a variety of web elements, for example, data graphics and elements, to present the structural effect of these variables on the price of diamonds. Therefore, by including necessary content and web elements and employing the formatting to present the structural effects, we met the Markdown standard.
- `r standard_button("aesthetics")`: In terms of our data graphics, we used line charts to showcase the effects of the determinants on the diamonds prices. Because our graphs are two-dimensional, we dropped the effect of cut in our presentation for the reason that the graphs would be clearer with the selected four variables rather than five. In addition, we used different colored lines in the graphs to differentiate color and clarity intensities. Also, sincfe these colored lines are light colors, we used black as the background color and kept white as the word color. Thus, with customized graphics which reflect the underlying data, we met the Aesthetics standard.
